Technical Report

### 2017-12-12 fully-abstract-comp/technical-report.tex
Answered Dominique's comments and made a few related updates

\subsection{Syntax}
\label{sec:syntax}
The target machine is a simple capability machine with memory capabilities and sealed capabilities\footnote{In previous work, we used enter capabilities but for this the complexity introduced by mixing writable and executable memory is difficult to handle.} (inspired by CHERI). The syntax of the instructions of the target machine is defined as follows:
\[
\begin{array}{rcl}
n &\in & \nats \\
\trg{r} &\in &  \tRegName \\
\trg{\rn} &\defbnf &  \trg{r} \mid n \\
\trg{i} &\defbnf & \tfail \mid \thalt \mid \tjmp{\trg{r}} \mid \tjnz{\trg{r}}{\trg{\rn}} \mid \tisptr{\trg{r}}{\trg{r}} \mid \tgeta{\trg{r}}{\trg{r}} \mid \tgetb{\trg{r}}{\trg{r}} \mid \\
      & &  \tgete{\trg{r}}{\trg{r}}\mid \tgetp{\trg{r}}{\trg{r}} \mid \tgetlin{\trg{r}}{\trg{r}} \mid \tmove{\trg{r}}{\trg{\rn}} \mid \tstore{\trg{r}}{\trg{r}} \mid\\
      & &  \tload{\trg{r}}{\trg{r}} \mid \tcca{\trg{r}}{\trg{\rn}} \mid \trestrict{\trg{r}}{\trg{r}}{\trg{\rn}} \mid \tlt{\trg{r}}{\trg{r}}{\trg{r}} \mid \\
  & & \tplus{\trg{r}}{\trg{\rn}}{\trg{\rn}} \mid \tminus{\trg{r}}{\trg{\rn}}{\trg{\rn}} \mid \tsetatob{\trg{r}}{\trg{r}} \mid \txjmp{\trg{r}}{\trg{r}} \mid \tcseal{\trg{r}}{\trg{r}}{\trg{r}} \mid \\ 
      & &   \tsplit{\trg{r}}{\trg{r}}{\trg{r}}{\trg{\rn}} \mid\tsplice{\trg{r}}{\trg{r}}{\trg{r}} 
\end{array}
\]
$i$ defines the set $\Instr$

@@

\subsubsection{Helpful functions and sets}

\[
  \pi_\baddr(\vsc) =
  \begin{cases}
    \baddr & \text{if $\vsc = ((\_,\_),\baddr,\_,\_)$} \\ 
    \pi_\baddr(c) & \text{if $\vsc = \sealed{\_,c}$} \\ 
    \src{\baddr} & \src{\text{if $\vsc = \stkptr{\_,\baddr,\_,\_}$}} \\ 
    \src{\baddr} & \src{\text{if $\vsc = \retptrd{\_,(\baddr,\_)}$}} \\ 
    \src{\baddr} & \src{\text{if $\vsc = \retptrc{\_,(\_,\_,\baddr,\_,\_)}$}}
  \end{cases}
\]
\[
  \pi_\eaddr(\vsc) =
  \begin{cases}
    \eaddr & \text{if $\vsc = ((\_,\_),\_,\eaddr,\_)$} \\ 
    \pi_\eaddr(c) & \text{if $\vsc = \sealed{\_,c}$} \\ 
    \src{\eaddr} & \src{\text{if $\vsc = \stkptr{\_,\_,\eaddr,\_}$}} \\ 
    \src{\eaddr} & \src{\text{if $\vsc = \retptrd{\_,(\_,\eaddr)}$}} \\ 
    \src{\eaddr} & \src{\text{if $\vsc = \retptrc{\_,(\_,\_,\_,\eaddr,\_)}$}}
  \end{cases}
\]
\[
  \pi_\lin(\vsc) = 
  \begin{cases}
    \lin & \text{if $\vsc = ((\_,\_),\_,\eaddr,\_)$} \\ 
    \pi_\lin(c) & \text{if $\vsc = \sealed{\_,c}$} \\ 
    \src{\linear} & \src{\text{if $\vsc = \stkptr{\_,\_,\eaddr,\_}$}} \\ 
    \src{\linear} & \src{\text{if $\vsc = \retptrd{\_,(\_,\_)}$}} \\ 
    \src{\lin} & \src{\text{if $\vsc = \retptrc{\_,(\_,\lin,\_,\_,\_)}$}}
  \end{cases}
\]

\dominique{4-12-2017: what about $\pi_a$?}

\[
  \updPcAddr{c} \defeq \dots
\]

@@

@@

\noindent\textbf{fail and halt}\\
\begin{align*}
  \sem{\tfail}(\Phi) = & \; \failed \\
  \sem{\thalt}(\Phi) = & \; \halted
\end{align*}

@@

\begin{align*}
  \sem{\tgetlin{r_1}{r_2}}(\Phi) = & 
                                   \begin{cases}
                                     \updPcAddr{\Phi\updReg{r_1}{\lin}} & 
                                     \arraycolsep=0pt
                                     \begin{array}[t]{l}
                                       \Phi(r_2) = ((\_,\lin),\_,\_,\_) \\
                                       \quad \tor \Phi(r_2) = \seal{\lin,\_,\_,\_} \\
                                       \quad \src{\tor \Phi(r_2) = \stkptr{\_,\_,\_,\_} \tand l = \linear}\\
                                     \end{array} \\
                                     \updPcAddr{\Phi\updReg{r_1}{-1}} & \totherwise
                                   \end{cases}
\end{align*}
\lau{15-09-2017: Should getl do something for seals?}
\dominique{4-12-2017: doesn't matter, I think.}
\lau{15-09-2017: Do we want to allow getl and getp to work on sealed capabilities?}
\dominique{Linearity of sealed caps is already observable anyway, so no point in hiding it.  Permissions of the sealed capability should be hidden, I think, mostly out of conservativity (hide as much as possible!).}
\dominique{4-12-2017: Couldn't the definitions above use $\pi_b$, $\pi_e$, $\pi_l$ and $\pi_a$ and $\pi_p$ (the latter two to be added) ?}

@@

\emph{Change Current Address}
\lau{15-09-2017: This is the old lea. I changed the name, so it actually reflects what the instruction does. We might also want to add a real lea at some point.}
\begin{align*}
  \sem{\tcca{r}{\rn}}(\Phi) = & 
                                  \begin{cases}
                                    \updPcAddr{\Phi\updReg{r}{c}} &  
                                    \arraycolsep=0pt
                                    \begin{array}[t]{l}
                                      \text{either $n = \rn$ or $n = \Phi.\reg(\rn)$}\\
                                      \quad\text{ and in either case $n \in \ints$ and} \\
                                      \Phi(r) = ((\perm,\lin),\baddr,\eaddr,\aaddr) \tand \\
                                      c = ((\perm,\lin),\baddr,\eaddr,\aaddr + n)
                                    \end{array}
                                    \\
                                    \updPcAddr{\Phi\updReg{r}{c}} &  
                                    \arraycolsep=0pt
                                    \begin{array}[t]{l}
                                      \text{either $n = \rn$ or $n = \Phi.\reg(\rn)$}\\
                                      \quad\text{ and in either case $n \in \ints$ and} \\
                                      \Phi(r) = \seal{\lin,\sigma_\baddr,\sigma_\eaddr,\sigma} \tand \\
                                      c = \seal{\lin,\sigma_\baddr,\sigma_\eaddr,\sigma + n}
                                    \end{array}
                                    \\
                                    \src{\updPcAddr{\Phi\updReg{r}{c}}} &  
                                    \sourcecolor\left.
                                    \arraycolsep=0pt
                                    \begin{array}[t]{l}
                                      \text{either $n = \rn$ or $n = \Phi(\rn)$}\\
                                      \quad\text{ and in either case $n \in \ints$ and} \\
                                      \Phi(r) = \stkptr{\perm,\baddr,\eaddr,\aaddr} \tand \\
                                      c = \stkptr{\perm,\baddr,\eaddr,\aaddr + n}
                                    \end{array}\right.
                                    \\
                                    \failed & \totherwise
                                  \end{cases}
\end{align*}

\noindent\textbf{restrict}\\
This instruction uses the $\decPerm{}$ function.
\begin{align*}
  \sem{\trestrict{r_1}{r_2}{\rn}} = &
                                      \begin{cases}
                                        \updPcAddr{}\left(
                                          \arraycolsep=0pt
                                          \begin{array}{rl}
                                          \Phi&\updReg{r_2}{w_2}\\
                                              &\updReg{r_1}{c}
                                          \end{array} \right)
&
                                        \arraycolsep=0pt
                                        \begin{array}[t]{l}
                                          \Phi(r_2) = ((\perm,\lin),\baddr,\eaddr,\aaddr) \tand \\
                                          \text{either $n = \rn$ or $n = \Phi.\reg(\rn)$}\\
                                          \quad\text{and in either case $n \in \ints$ and} \\
                                          \decPerm{n} \sqsubseteq \perm \tand \\
                                          c = ((\decPerm{n},\lin),\baddr,\eaddr,\aaddr) \tand \\
                                          w_2 = \linCons{\Phi(r_2)}
                                        \end{array}
                                        \\
                                        \sourcecolor\left.
                                        \updPcAddr{}\left(
                                          \arraycolsep=0pt
                                          \begin{array}{rl}
                                          \Phi&\updReg{r_2}{0}\\
                                                    &\updReg{r_1}{c}
                                          \end{array}\right)\right.
                                        &
                                        \sourcecolor\left.
                                        \arraycolsep=0pt
                                        \begin{array}[t]{l}
                                          \Phi(r_2) = \stkptr{\perm,\baddr,\eaddr,\aaddr} \tand \\
                                          \text{either $n = \rn$ or $n = \Phi.\reg(\rn)$}\\
                                          \quad\text{and in either case $n \in \ints$ and} \\
                                          \decPerm{n} \sqsubseteq \perm \tand \\
                                          c = \stkptr{\decPerm{n},\baddr,\eaddr,\aaddr}
                                        \end{array}\right.
                                        \\
                                        \failed & \totherwise
                                      \end{cases}
\end{align*}

\noindent\textbf{lt}\\
\begin{align*}
  \sem{\tlt{r_0}{r_1}{r_2}}(\Phi) = &
                                                  \begin{cases}
                                                    \updPcAddr{\Phi\updReg{r_0}{1}} &
                                                    \arraycolsep=0pt
                                                    \begin{array}[t]{l}
                                                      \text{if for $i \in \{1,2\}$}\\
                                                      \quad\text{$n_i = r_i$ or $n_i = \Phi(r_i)$}\\
                                                      \quad\text{and in either case $n_i \in \ints$}\\
                                                      \quad\text{and $n_1 < n_2$}\\        
                                                    \end{array}\\
                                                    \updPcAddr{\Phi\updReg{r_0}{0}} &
                                                    \arraycolsep=0pt
                                                    \begin{array}[t]{l}
                                                      \text{if for $i \in \{1,2\}$}\\
                                                      \quad\text{$n_i = r_i$ or $n_i = \Phi(r_i)$}\\
                                                      \quad\text{and in either case $n_i \in \ints$}\\
                                                      \quad\text{and $n_1 \not< n_2$}\\        
                                                    \end{array}\\
                                                    \failed & \text{otherwise}
                                                  \end{cases}  
\end{align*}

\noindent\textbf{plus and minus}\\
\begin{align*}
  \sem{\tplus{r_0}{\rn_1}{\rn_2}}(\Phi) = &
                                                  \begin{cases}
                                                    \updPcAddr{\Phi\updReg{r_0}{n_1+n_2}} &
                                                    \arraycolsep=0pt
                                                    \begin{array}[t]{l}
                                                      \text{if for $i \in \{1,2\}$}\\
                                                      \quad\text{$n_i = \rn_i$ or $n_i = \Phi(\rn_i)$}\\
                                                      \quad\text{and in either case $n_i \in \ints$}\\
                                                    \end{array}\\
                                                    \failed & \text{otherwise}
                                                  \end{cases}  
\end{align*}

\begin{align*}
  \sem{\tminus{r_0}{\rn_1}{\rn_2}}(\Phi) = &
                                                  \begin{cases}
                                                    \updPcAddr{\Phi\updReg{r_0}{n_1-n_2}} &
                                                    \arraycolsep=0pt
                                                    \begin{array}[t]{l}
                                                      \text{if for $i \in \{1,2\}$}\\
                                                      \quad\text{$n_i = \rn_i$ or $n_i = \Phi(\rn_i)$}\\
                                                      \quad\text{and in either case $n_i \in \ints$}\\
                                                    \end{array}\\
                                                    \failed & \text{otherwise}
                                                  \end{cases}  
\end{align*}

@@

                                   \Phi(\rn_4) = n \tor \rn_4 = n \\
                                   \quad\text{ and in either case } n \in \nats \\

@@

                                   \Phi(\rn_4) = n \tor \rn_4 = n \\
                                   \quad\text{ and in either case } n \in \nats \\

@@

                                                   \ms_{\stk,\priv} = \ms_\stk |_{[\aaddr_\stk,\eaddr_\stk]}\update{\aaddr_\stk}{\eaddr_\stk} \tand\\

@@

>>>>

\subsection{Syntax}
\label{sec:syntax}
The target machine is a simple capability machine with memory capabilities and sealed capabilities\footnote{In previous work, we used enter capabilities but for this the complexity introduced by mixing writable and executable memory is difficult to handle.} (inspired by CHERI). The syntax of the instructions of the target machine is defined as follows:
\[
\begin{array}{rcl}
n &\in & \ints \\
\trg{r} &\in &  \tRegName \\
\trg{\rn} &\defbnf &  \trg{r} \mid n \\
\trg{i} &\defbnf & \tfail \mid \thalt \mid \tjmp{\trg{r}} \mid \tjnz{\trg{r}}{\trg{\rn}} \mid \tisptr{\trg{r}}{\trg{r}} \mid \tgeta{\trg{r}}{\trg{r}} \mid \tgetb{\trg{r}}{\trg{r}} \mid \\
      & &  \tgete{\trg{r}}{\trg{r}}\mid \tgetp{\trg{r}}{\trg{r}} \mid \tgetlin{\trg{r}}{\trg{r}} \mid \tmove{\trg{r}}{\trg{\rn}} \mid \tstore{\trg{r}}{\trg{r}} \mid\\
      & &  \tload{\trg{r}}{\trg{r}} \mid \tcca{\trg{r}}{\trg{\rn}} \mid \trestrict{\trg{r}}{\trg{r}}{\trg{\rn}} \mid \tlt{\trg{r}}{\trg{\rn}}{\trg{\rn}} \mid \\
  & & \tplus{\trg{r}}{\trg{\rn}}{\trg{\rn}} \mid \tminus{\trg{r}}{\trg{\rn}}{\trg{\rn}} \mid \tsetatob{\trg{r}}{\trg{r}} \mid \txjmp{\trg{r}}{\trg{r}} \mid \tcseal{\trg{r}}{\trg{r}}{\trg{r}} \mid \\ 
      & &   \tsplit{\trg{r}}{\trg{r}}{\trg{r}}{\trg{\rn}} \mid\tsplice{\trg{r}}{\trg{r}}{\trg{r}} 
\end{array}
\]
$i$ defines the set $\Instr$

@@

\subsubsection{Helpful functions, sets, and conventions}

\[
  \pi_\baddr(\vsc) =
  \begin{cases}
    \baddr & \text{if $\vsc = ((\_,\_),\baddr,\_,\_)$} \\ 
    \pi_\baddr(c) & \text{if $\vsc = \sealed{\_,c}$} \\ 
    \src{\baddr} & \src{\text{if $\vsc = \stkptr{\_,\baddr,\_,\_}$}} \\ 
    \src{\baddr} & \src{\text{if $\vsc = \retptrd{\_,(\baddr,\_)}$}} \\ 
    \src{\baddr} & \src{\text{if $\vsc = \retptrc{\_,(\_,\_,\baddr,\_,\_)}$}}
  \end{cases}
\]
\[
  \pi_\eaddr(\vsc) =
  \begin{cases}
    \eaddr & \text{if $\vsc = ((\_,\_),\_,\eaddr,\_)$} \\ 
    \pi_\eaddr(c) & \text{if $\vsc = \sealed{\_,c}$} \\ 
    \src{\eaddr} & \src{\text{if $\vsc = \stkptr{\_,\_,\eaddr,\_}$}} \\ 
    \src{\eaddr} & \src{\text{if $\vsc = \retptrd{\_,(\_,\eaddr)}$}} \\ 
    \src{\eaddr} & \src{\text{if $\vsc = \retptrc{\_,(\_,\_,\_,\eaddr,\_)}$}}
  \end{cases}
\]

\[
  \pi_\lin(\vsc) = 
  \begin{cases}
    \lin & \text{if $\vsc = ((\_,\_),\_,\eaddr,\_)$} \\ 
    \pi_\lin(c) & \text{if $\vsc = \sealed{\_,c}$} \\ 
    \src{\linear} & \src{\text{if $\vsc = \stkptr{\_,\_,\eaddr,\_}$}} \\ 
    \src{\linear} & \src{\text{if $\vsc = \retptrd{\_,(\_,\_)}$}} \\ 
    \src{\lin} & \src{\text{if $\vsc = \retptrc{\_,(\_,\lin,\_,\_,\_)}$}}
  \end{cases}
\]

\dominique{4-12-2017: what about $\pi_a$?}
\lau{12-12-2017: I have added them as I needed them in the LR. I have not needed $\pi_a$ yet.}
\[
  \updPcAddr{c} \defeq \dots
\]

@@

For $\rn$ which can be a register or an integer, we take
\[
  \Phi(\rn) = n
\]
to mean
\[
  \text{either $n = \rn$ or $n = \Phi.\reg(\rn)$ and in either case $n \in \ints$}
\]

@@

\noindent\textbf{fail and halt}\\
\begin{align*}
  \sem{\tfail}(\Phi) = & \; \failed \\
  \sem{\thalt}(\Phi) = & \; \haltde
\end{align*}

@@

\begin{align*}
  \sem{\tgetlin{r_1}{r_2}}(\Phi) = & 
                                   \begin{cases}
                                     \updPcAddr{\Phi\updReg{r_1}{\lin}} & 
                                     \arraycolsep=0pt
                                     \begin{array}[t]{l}
                                       \Phi(r_2) = ((\_,\lin),\_,\_,\_) \\
                                       \quad \tor \Phi(r_2) = \seal{\lin,\_,\_,\_} \\
                                       \quad \src{\tor \Phi(r_2) = \stkptr{\_,\_,\_,\_} \tand l = \linear}\\
                                     \end{array} \\
                                     \updPcAddr{\Phi\updReg{r_1}{-1}} & \totherwise
                                   \end{cases}
\end{align*}
\lau{15-09-2017: Should getl do something for seals?}
\dominique{4-12-2017: doesn't matter, I think.}
\lau{15-09-2017: Do we want to allow getl and getp to work on sealed capabilities?}
\dominique{Linearity of sealed caps is already observable anyway, so no point in hiding it.  Permissions of the sealed capability should be hidden, I think, mostly out of conservativity (hide as much as possible!).}
\dominique{4-12-2017: Couldn't the definitions above use $\pi_b$, $\pi_e$, $\pi_l$ and $\pi_a$ and $\pi_p$ (the latter two to be added) ?}
\lau{12-12-2017: $\pi_\_$ also projects from sealed capabilities, so the case of sealed capabilities would have to be explicitely excluded (with getl as the exception).}

@@

\emph{Change Current Address}
\lau{15-09-2017: This is the old lea. I changed the name, so it actually reflects what the instruction does. We might also want to add a real lea at some point.}
\begin{align*}
  \sem{\tcca{r}{\rn}}(\Phi) = & 
                                  \begin{cases}
                                    \updPcAddr{\Phi\updReg{r}{c}} &  
                                    \arraycolsep=0pt
                                    \begin{array}[t]{l}
                                      \Phi(\rn) = n \tand \\
                                      \Phi(r) = ((\perm,\lin),\baddr,\eaddr,\aaddr) \tand \\
                                      c = ((\perm,\lin),\baddr,\eaddr,\aaddr + n)
                                    \end{array}
                                    \\
                                    \updPcAddr{\Phi\updReg{r}{c}} &  
                                    \arraycolsep=0pt
                                    \begin{array}[t]{l}
                                      \Phi(\rn) = n \tand \\
                                      \Phi(r) = \seal{\lin,\sigma_\baddr,\sigma_\eaddr,\sigma} \tand \\
                                      c = \seal{\lin,\sigma_\baddr,\sigma_\eaddr,\sigma + n}
                                    \end{array}
                                    \\
                                    \src{\updPcAddr{\Phi\updReg{r}{c}}} &  
                                    \sourcecolor\left.
                                    \arraycolsep=0pt
                                    \begin{array}[t]{l}
                                      \Phi(\rn) = n\tand \\
                                      \Phi(r) = \stkptr{\perm,\baddr,\eaddr,\aaddr} \tand \\
                                      c = \stkptr{\perm,\baddr,\eaddr,\aaddr + n}
                                    \end{array}\right.
                                    \\
                                    \failed & \totherwise
                                  \end{cases}
\end{align*}

\noindent\textbf{restrict}\\
This instruction uses the $\decPerm{}$ function.
\begin{align*}
  \sem{\trestrict{r_1}{r_2}{\rn}} = &
                                      \begin{cases}
                                        \updPcAddr{}\left(
                                          \arraycolsep=0pt
                                          \begin{array}{rl}
                                          \Phi&\updReg{r_2}{w_2}\\
                                              &\updReg{r_1}{c}
                                          \end{array} \right)
&
                                        \arraycolsep=0pt
                                        \begin{array}[t]{l}
                                          \Phi(r_2) = ((\perm,\lin),\baddr,\eaddr,\aaddr) \tand \\
                                          \Phi(\rn) = n \tand\\
                                          \decPerm{n} \sqsubseteq \perm \tand \\
                                          c = ((\decPerm{n},\lin),\baddr,\eaddr,\aaddr) \tand \\
                                          w_2 = \linCons{\Phi(r_2)}
                                        \end{array}
                                        \\
                                        \sourcecolor\left.
                                        \updPcAddr{}\left(
                                          \arraycolsep=0pt
                                          \begin{array}{rl}
                                          \Phi&\updReg{r_2}{0}\\
                                                    &\updReg{r_1}{c}
                                          \end{array}\right)\right.
                                        &
                                        \sourcecolor\left.
                                        \arraycolsep=0pt
                                        \begin{array}[t]{l}
                                          \Phi(r_2) = \stkptr{\perm,\baddr,\eaddr,\aaddr} \tand \\
                                          \Phi(\rn) = n \tand\\
                                          \decPerm{n} \sqsubseteq \perm \tand \\
                                          c = \stkptr{\decPerm{n},\baddr,\eaddr,\aaddr}
                                        \end{array}\right.
                                        \\
                                        \failed & \totherwise
                                      \end{cases}
\end{align*}

\noindent\textbf{lt}\\
\begin{align*}
  \sem{\tlt{r_0}{\rn_1}{\rn_2}}(\Phi) = &
                                                  \begin{cases}
                                                    \updPcAddr{\Phi\updReg{r_0}{1}} &
                                                    \arraycolsep=0pt
                                                    \begin{array}[t]{l}
                                                      \text{if for $i \in \{1,2\}$}\\
                                                      \quad\Phi(\rn_i) = n_i \tand\\
                                                      \quad\text{and $n_1 < n_2$}\\        
                                                    \end{array}\\
                                                    \updPcAddr{\Phi\updReg{r_0}{0}} &
                                                    \arraycolsep=0pt
                                                    \begin{array}[t]{l}
                                                      \text{if for $i \in \{1,2\}$}\\
                                                      \quad \Phi(\rn_i) = n_i \tand \\
                                                      \quad\text{and $n_1 \not< n_2$}\\        
                                                    \end{array}\\
                                                    \failed & \text{otherwise}
                                                  \end{cases}  
\end{align*}

\noindent\textbf{plus and minus}\\
\begin{align*}
  \sem{\tplus{r_0}{\rn_1}{\rn_2}}(\Phi) = &
                                                  \begin{cases}
                                                    \updPcAddr{\Phi\updReg{r_0}{n_1+n_2}} &
                                                    \arraycolsep=0pt
                                                    \begin{array}[t]{l}
                                                      \text{if for $i \in \{1,2\}$}\\
                                                      \quad \Phi(\rn_i) = n_i\\
                                                    \end{array}\\
                                                    \failed & \text{otherwise}
                                                  \end{cases}  
\end{align*}

\begin{align*}
  \sem{\tminus{r_0}{\rn_1}{\rn_2}}(\Phi) = &
                                                  \begin{cases}
                                                    \updPcAddr{\Phi\updReg{r_0}{n_1-n_2}} &
                                                    \arraycolsep=0pt
                                                    \begin{array}[t]{l}
                                                      \text{if for $i \in \{1,2\}$}\\
                                                      \quad\Phi(\rn_i) = n_i\\
                                                    \end{array}\\
                                                    \failed & \text{otherwise}
                                                  \end{cases}  
\end{align*}

@@

                                   \Phi(\rn_4) = n \tand\\

@@

                                   \Phi(\rn_4) = n \tand \\

@@

                                                   \ms_{\stk,\priv} = \ms_\stk |_{[\aaddr_\stk,\eaddr_\stk]}\update{\aaddr_\stk}{42} \tand\\

@@

\lau{12-12-2017: Correct. Please feel free to correct these things.}
